---
title: "Teach me shiny (with trees)"
author: "Till Straube"
date: "August 20, 2020"
output: html_document
---

# Setup

```{r setup, message=F}
load("trees.Rdata")
library(tidyverse)
knitr::opts_chunk$set(cache=T, warning=F, fig.align='center', out.width='90%')
```

# Quick variable reference

Variable          | Type           | Content
:-------          | :----          | :---------
Pflanzjahr        | *double*       | Year of planting
Kronendurchmesser | *double*       | Diameter of the treetop in meters (contains some questionable values)
Gattung           | *factor (int)* | Best guess of the species (German name) of the tree (extracted from more complex string)
Typ               | *factor (int)* | One of "Obst-/Nussbaum" (fruit-/nut-bearing trees), "Laubbaum" (other decidious trees) or "Nadelbaum" (conifers)
Stadtteil         | *factor (int)* | Name of the municipal administrative unit (arrived at by `st_join` with shapefile)
Objekt            | *char*         | Some sort of designator for the location (street, park)
geometry          | *list*         | Holds geodata in Simple Features format (EPSG 32632)

# Overview

```{r sample}
sample_n(trees, 5) %>%
  knitr::kable("html") %>%
  kableExtra::kable_styling()

trees %>%
  select(-geometry) %>%
  summary()
```

# Some visualization ideas

```{r heatmap}
table(trees$Gattung, trees$Stadtteil) %>%
  heatmap(col=colorRampPalette(RColorBrewer::brewer.pal(9, "YlGn"))(256))
```

```{r map}
stadtteile %>%
  sf::st_union() %>%
  sf::st_make_grid(n=25, square=F) %>%
  sf::st_as_sf() %>%
  mutate(`Bäume`=sf::st_covers(., trees) %>% lengths) -> hex_grid

ggplot(hex_grid) +
  geom_sf(aes(fill=Bäume), color=NA) +
  scale_fill_viridis_c() +
  theme_void()
```

# Lots of species

```{r alter}
trees %>%
  mutate(Alter = 2020 - Pflanzjahr) %>%
  ggplot() +
    geom_point(aes(x=Alter, y=Kronendurchmesser, color=Gattung)) +
    theme_minimal()
```

```{r densities}
trees %>%
  select(Gattung, Pflanzjahr) %>%
  remove_missing() %>%
  ggplot() +
    geom_density(aes(x=Pflanzjahr, fill=Gattung), color=NA, alpha=0.3) +
    scale_x_continuous(limits = c(1850, 2020)) +
    theme_minimal() +
    theme(legend.position="bottom")
```

# A starting point?

```{r hist}
trees %>%
  filter(Gattung=="Platane") %>%
  ggplot() +
    geom_histogram(aes(x=Pflanzjahr), bins=20) +
    theme_minimal()
```
